State of the Art Review on Privacy-Preserving Authentication

### 2021-11-29 prism-backend/research/soa_review/ac.tex
Pass to improve readability.

Restricting the expressiveness, and focusing on letting the credential holder
reveal only a subset of the attributes in a credential, more efficient schemes
have been proposed, leveraging algebraic tricks such as structure-preserving
signatures on equivalence classes (SPS-EQ), along with vector commitment schemes
\cite{cdhk15}, or set commitment schemes \cite{fhs19}. The former uses Lagrange
interpolation to allow revealing only a subset of the committed messages;
while \cite{fhs19} employs set commitment schemes, mapping the attributes to
be committed to roots of a polynomial, so that opening a specific subset of the
commmitted elements just requires revealing a subset of the roots of the
polynomial.
%
Also improving efficiency, but restricting to the scenario in which the issuer
is the same entity as the verifier (as in ticketing systems for public transport),
\cite{cmz14}, replaces signatures with algebraic MACs.

@@

\subsubsection{Efficiency.}
%

\subsubsection{Main challenges and interesting lines of work.}
%
\note{I find interesting that, given that ACs and group signatures are
  essentially the same thing, there is no work (or I have not come across it)
  trying to connect both. Specifically, the following questions:}

\begin{itemize}
\item Anonymity properties in ACs and GSs are roughly similar. However, concerning
  unforgeability-related properties:
  \begin{itemize}
  \item The notion of traceability in GSs seems incompatible in AC systems that
    do not include a user secret key in the credentials. Even for AC systems that
    do include it, unforgeability in AC is different than traceability, as there
    is no guarantee that a credential can be traced to a ``join'' process. Or
    there is?
  \item The notion of non-frameability of GSs does not seem to have an equivalent
    in ACs. I find this kind of surprising from a practical point of view, as an
    adversary in AC systems can very well aim at impersonating an honest user,
    which may then carry consequences (e.g., legal actions) for the honest user.
  \item Maybe I'm wrong in the two previous points, and we can draw a connection
    between (some basic notion of) unforgeability in ACs, and the usual notions
    of traceability and non-frameability in GSs. If I recall correctly, the
    \cite{bmw03} paper merged non-frameability and traceability into
    unforgeability, and this was later divided again in \cite{bsz05}. Check the
    reasoning again...
  \end{itemize}  
\item I find very surprising that essentially all the body of work in ACs is
  based on what seems to be the sign-randomize-proof approach of GSs, yet there
  is nothing (or I have not seen it) similar to the encrypt-then-prove approach.
  Can we do it? This may be due to the fact that revocation has not been
  considered as a main requirement in ACs (which, IMHO, is a drawback if we want
  systems applicable in the real world).
  \begin{itemize}
  \item Can we come up with a black-box construction of ACs from GSs, or vice
    versa? It should not be hard, and this may open a completely new breed of
    ACs (i.e., those based on the encrypt-then-prove approach).
  \end{itemize}
\end{itemize}

@@

>>>>

Restricting the expressiveness, and focusing on letting the credential holder
reveal only a subset of the attributes in a credential, more efficient schemes
have been proposed, leveraging algebraic tricks such as structure-preserving
signatures on equivalence classes (SPS-EQ), along with vector commitment schemes
\cite{cdhk15}, or set commitment schemes \cite{fhs19}. The former uses Lagrange
interpolation to allow revealing only a subset of the committed messages;
while \cite{fhs19} employs set commitment schemes, mapping the attributes to
be committed to roots of a polynomial, so that opening a specific subset of the
commmitted elements just requires revealing a subset of the roots of the
polynomial.
%
Also improving efficiency, but restricting to the scenario in which the issuer
is the same entity as the verifier (as in ticketing systems for public transport),
\cite{cmz14} replaces signatures with algebraic MACs.

@@

\subsubsection{Efficiency.}
%
\comment{This section is just a placeholder for now...}

\subsubsection{Main challenges and interesting lines of work.}
%
\comment{This section is just a placeholder for now...}

I find interesting that, given that ACs and group signatures are
essentially the same thing, there is no work (or I have not come across it)
trying to connect both. Specifically, the following questions:

\begin{itemize}
\item Anonymity properties in ACs and GSs are roughly similar. However, concerning
  unforgeability-related properties:
  \begin{itemize}
  \item The notion of traceability in GSs seems incompatible in AC systems that
    do not include a user secret key in the credentials. Even for AC systems that
    do include it, unforgeability in AC is different than traceability, as there
    is no guarantee that a credential can be traced to a ``join'' process. Or
    there is?
  \item The notion of non-frameability of GSs does not seem to have an equivalent
    in ACs. I find this kind of surprising from a practical point of view, as an
    adversary in AC systems can very well aim at impersonating an honest user,
    which may then carry consequences (e.g., legal actions) for the honest user.
    Probably, this is related to ACs not having opening, although it has been
    shown in the GS literature that schemes without opening, but with linking
    can still have a notion of non-frameability \cite{dl21} (and, certainly,
    blacklisting/revocation allows linking, and this has already been done in
    the AC domain.)
  \item Maybe I'm wrong in the two previous points, and we can draw a connection
    between (some basic notion of) unforgeability in ACs, and the usual notions
    of traceability and non-frameability in GSs. If I recall correctly, the
    \cite{bmw03} paper merged non-frameability and traceability into
    unforgeability, and this was later divided again in \cite{bsz05}. Check the
    reasoning again...
  \end{itemize}  
\item I find very surprising that essentially all the body of work in ACs is
  based on what seems to be the sign-randomize-proof approach of GSs, yet there
  is nothing (or I have not seen it) similar to the encrypt-then-prove approach.
  Can we do it? This may be due to the fact that revocation has not been
  considered as a main requirement in ACs (which, IMHO, is a drawback if we want
  systems applicable in the real world).
  \begin{itemize}
  \item Can we come up with a black-box construction of ACs from GSs, or vice
    versa? It should not be hard, and this may open a completely new breed of
    ACs (i.e., those based on the encrypt-then-prove approach).
  \end{itemize}
\item Also, forward security does not seem to have been explored in the AC
  domain (again, I may just overlooked works on it). But it has been studied in
  GSs. Can we leverage that?
\end{itemize}

@@

\comment{This section is just a placeholder for now...}

### 2021-11-29 prism-backend/research/soa_review/gs.tex
Pass to improve readability.

\subsubsection{Variations in functionality.}
%
Note that, while the security properties just described roughly have the same
purpose across models, there are still differences making some models stronger
or more general than others in some respects. This includes subtleties like who
generates the keys of the authorities (the environment vs the adversary), how
many queries can be made to the challenge oracles and whether or not the
signatures are fixed, etc. However, while important, there are usually generic
techniques that allow to migrate from one variant to another \todo{\needcite,
  ellaborate more, or rewrite}. Now we are interested in revisiting some of
the variations that have impact into the functionality that schemes
following each model can provide, or variations that are specific to group
signatures schemes and do not appear in other cryptosystems.

@@

\note{Concurrent joins -- avoid extraction \cite{ky05,klap20}.}

>>>>

\subsubsection{Variations in functionality.}
%
Note that, while the security properties just described roughly have the same
purpose across models, there are still differences making some models stronger
or more general than others in some respects. This includes subtleties like who
generates the keys of the authorities (the environment vs the adversary), how
many queries can be made to the challenge oracles and whether or not the
signatures are fixed, etc. However, while important, there are usually generic
techniques that allow to migrate from one variant to another \needcite. Now we
are interested in revisiting some of
the variations that have impact into the functionality that schemes
following each model can provide, or variations that are specific to group
signatures schemes and do not appear in other cryptosystems.

@@

Concurrent joins -- avoid extraction \cite{ky05,klap20}.

### 2021-11-29 prism-backend/research/soa_review/soa-review.tex
Review of FHS19.
Some writeup on ACs main approaches, security models, and functionality. Doc reorg.
Polished version. Still early draft, but at least readable (excluding DAA section, which is not a priority for now).
Pass to improve readability.

\title{State of the Art Review on Privacy-Preserving Signatures, Credentials, and Authentication}
\author{}

@@

\begin{abstract}
	\textbf{DISCLAIMER}: Please, keep in mind that, as of now, this document
	basically contains a research log in the shape of personal notes. Do not take 
	anything written here as ground truth.
\end{abstract}

\input{introduction.tex}
\input{gs.tex}
\input{abs.tex}
\input{ac.tex}
\input{daa.tex}
\input{other.tex}
\input{discussion.tex}
\input{conclusion.tex}

@@

\begin{itemize}
\item Many constructions of ACs and GSs seem to be built using the same
  approach: an issuer and a user interact so that the latter receives a signature
  from the former; then the user employs that signature to do something else (in
  ACs, prove attributes; in GSs, produce further signatures). Still, the typical
  security models are different. Concretely, GSs have a very well established
  model, but ACs don't. It also ``bothers'' me that none of the AC models I've
  seen cover something similar to non-frameability, nor traceability, but just
  include conventional unforgeability properties. Why is this?
  \begin{itemize}
  \item Concerning non-frameability, this probably is because the de-anonymizing
    functionality that ACs include (if any) is revocation, which is essentially
    a blacklisting. On the other hand, GSs usually allow opening, which extracts
    the actual identity. Opening is ``stronger'' than blacklisting, in the sense
    that it can be used to build blacklisting, but it is also more threatening
    to privacy and may have further implications. Among these, unequivocable
    framing of users. This, in general, does not seem possible with conventional
    blacklisting (or, at least, not in an unequivocable way).
  \item Concerning traceability.
  \end{itemize}
\end{itemize}

>>>>

\title{State of the Art Review on Privacy-Preserving Authentication}
\author{}

@@

\begin{abstract}
  \comment{\textbf{DISCLAIMER}: Please, keep in mind that this is a working
    draft. Its main use in its current state is to foster debate on the topics
    it deals with. Do not take anything written here as ground truth.}

  This document explores three closely related cryptographic systems in the area
  of privacy-enhanced and, more concretely, in the domain of authentication.
  Namely, we study advances in group signatures (GS), anonymous credentials
  (AC), and direct anonymous attestation (DAA). All three have somehow similar
  purpose, have followed similar approaches, and have received much attention in
  the the academic literature for the last (almost) four decades but, in some
  sense, independently on one another.

  Our goal is to extract common insight from all of them. Firstly, from a
  theoretical perspective, with the aim to identify the advantages and
  disadvantages of existing models and approaches, and develop intuition as to
  whether we can (or cannot) combine ideas and fill gaps, and what may be the
  most suitable path to follow for new projects, depending on their needs.
  Secondly, from a practical perspective, DAA and ACs have already been deployed
  in the real world, and analysing the difficulties they have come across will
  certainly be of use.

\end{abstract}

\iffalse
\input{introduction.tex}
\fi
\input{gs.tex}
%\input{abs.tex}
\input{ac.tex}
\input{daa.tex}
\input{other.tex}
\input{discussion.tex}
\input{conclusion.tex}

\appendix

@@

\begin{itemize}
\item Many constructions of ACs and GSs seem to be built using the same
  approach: an issuer and a user interact so that the latter receives a signature
  from the former; then the user employs that signature to do something else (in
  ACs, prove attributes; in GSs, produce further signatures). Still, the typical
  security models are different. Concretely, GSs have a very well established
  model, but ACs don't. It also ``bothers'' me that none of the AC models I've
  seen cover something similar to non-frameability, nor traceability, but just
  include conventional unforgeability properties. Why is this?
  \begin{itemize}
  \item Concerning non-frameability, this probably is because the de-anonymizing
    functionality that ACs include (if any) is revocation, which is essentially
    a blacklisting. On the other hand, GSs usually allow opening, which extracts
    the actual identity. Opening is ``stronger'' than blacklisting, in the sense
    that it can be used to build blacklisting, but it is also more threatening
    to privacy and may have further implications. Among these, unequivocable
    framing of users. This, in general, does not seem possible with conventional
    blacklisting (or, at least, not in an unequivocable way).
  \item Concerning traceability. \cite{fhs19} definition of unforgeability
    resembles traceability. I guess this would be the case in most AC works.
  \end{itemize}
\end{itemize}

\input{app-gs}
\input{app-ac}
